\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{amsmath}
\begin{document}
\section*{Documentation for module: complex.lua}
\subsection*{Constant: \_\_index}
Complex number library. Pure Lua complex arithmetic (LuaLaTeX oriented). Provides arithmetic, elementary functions, geometric utilities, and tolerant comparisons.  @module complex @author Damien Mégy @license CC0-1.0
\hrulefill

\subsection*{Constant: EPS\_INV}
precision
\hrulefill

\subsection*{Function: new}
Constructor 
\hrulefill

\subsection*{Function: polar}
Polar constructor.
\hrulefill

\subsection*{Function: isComplex}
----------------------------------------- Type checking and coercion -----------------------------------------
\hrulefill

\subsection*{Function: coerce}
Public coerce, handles various arguments
\hrulefill

\subsection*{Function: \_\_eq}
----------------------------------------- Arithmetic metamethods ----------------------------------------- Exact equality test (no tolerance). Use `isClose` for numerical comparisons.
\hrulefill

\subsection*{Function: \_\_add}
Addition metamethod.
\hrulefill

\subsection*{Function: \_\_sub}
Subtraction metamethod.
\hrulefill

\subsection*{Function: \_\_mul}
Multiplication metamethod.
\hrulefill

\subsection*{Function: \_\_div}
Division metamethod.
\textbf{Errors:}
\begin{itemize}
\item Division by zero.
\end{itemize}
\hrulefill

\subsection*{Function: \_\_unm}
Unary minus metamethod.
\hrulefill

\subsection*{Function: \_\_tostring}
----------------------------------------- Pretty printing ----------------------------------------- Convert to string in the form `a+bi`.
\hrulefill

\subsection*{Function: isClose}
----------------------------------------- Additional functions ----------------------------------------- Approximate equality (L¹ norm).
\textbf{Parameters:}
\begin{itemize}
\item \texttt{a} (complex) : 
\item \texttt{b} (complex) : 
\item \texttt{eps} (number) : optional tolerance
\end{itemize}
\textbf{Returns:}
\begin{itemize}
\item (boolean) : 
\end{itemize}
\hrulefill

\subsection*{Function: isClosePair}
Compare unordered pairs with tolerance.
\hrulefill

\subsection*{Function: distinct}
Test whether two numbers are distinct (tolerant).
\hrulefill

\subsection*{Function: nonzero}
Test whether a complex number is nonzero (tolerant).
\hrulefill

\subsection*{Function: det}
Determinant
\hrulefill

\subsection*{Function: dot}
Scalar (dot) product.
\hrulefill

\subsection*{Function: unit}
Normalize to unit modulus.
\textbf{Returns:}
\begin{itemize}
\item (complex|nil) : nil if zero
\end{itemize}
\hrulefill

\subsection*{Function: conj}
Complex conjugate.
\hrulefill

\subsection*{Function: abs2}
Squared modulus.
\hrulefill

\subsection*{Function: abs}
Modulus.
\hrulefill

\subsection*{Function: arg}
Argument (principal value). Returns angle in radians in (-π, π].
\hrulefill

\subsection*{Function: invert}
Complex inversion in circle.
\textbf{Parameters:}
\begin{itemize}
\item \texttt{z} (complex) : 
\item \texttt{center} (complex) : optional
\item \texttt{R} (number) : optional radius
\end{itemize}
\hrulefill

\subsection*{Function: isNear}
----------------------------------------- Comparisons (methods, with optional tolerance) ----------------------------------------- Approximate equality (method form).
\hrulefill

\subsection*{Function: isNot}
Negated approximate comparison (method form).
\hrulefill

\subsection*{Function: isInteger}
integer check, no tolerance
\hrulefill

\subsection*{Function: isReal}
Test whether imaginary part is approx. zero (method form).
\hrulefill

\subsection*{Function: isImag}
Test whether real part is approx. zero (method form).
\hrulefill

\subsection*{Function: isNearInteger}
Integer check with tolerance
\hrulefill

\subsection*{Function: isUnit}
Test whether modulus is approx. 1 (method form).
\hrulefill

\subsection*{Function: isColinear}
Test approx. colinearity with other number (method form).
\hrulefill

\subsection*{Function: toPolar}
Convert to polar coordinates.
\textbf{Returns:}
\begin{itemize}
\item (r) : number
\item (theta) : number
\end{itemize}
\hrulefill

\subsection*{Function: clone}
Note : returns (0,0) for origin Clone the complex number.
\hrulefill

\subsection*{Function: exp\_i}
e\^\{iθ\}
\hrulefill

\subsection*{Function: rotate90}
Rotate by 90 degrees.
\hrulefill

\subsection*{Function: rotate}
Rotate by angle θ (radians).
\hrulefill

\subsection*{Function: exp}
Complex exponential.
\hrulefill

\subsection*{Function: log}
Principal complex logarithm.
\textbf{Errors:}
\begin{itemize}
\item undefined for 0
\end{itemize}
\hrulefill

\subsection*{Function: \_\_pow}
Note : other languages return -inf+0*i fast integer power (binary exponentiation) Power metamethod. Handles integer and complex exponents.
\hrulefill

\subsection*{Constant: ONE}
Special cases (approx) integer exponent. Is rounding a good idea ? General complex power  Constants 
\hrulefill

\end{document}